AIR4Children: Artificial Intelligence and Robotics for Children

### 2021-02-14 article/tex/submission.tex
poslishes conclusions

That said, figure \ref{fig:tm}(a) illustrates the spiral learning technique adopted for AIR4Children to reinforce the above Montessori skills \cite{tarik2017}.

%Finding solutions together translate to social situations as well as it provides children with the foundations for decision making, logical reasoning, categorizing, analytical thinking, negotiation, and creativity. 
%In that way, AIR4Children's workshop integrates various hands-on activities where the children will develop different intellectual and social skills to incorporate into other areas of their lives.
%More specifically, such workshops are based on several Montessori principles such as: moving from the simple to the complex, the concrete to the abstract, the familiar to the unfamiliar and the general to the specific, as well as a mixed age group, where children can learn from each other.
\begin{figure}[h]
  \centering
  \includegraphics[width=\linewidth]{../figures/teaching-materials/versions/drawing-v00.png}
  \caption{(a) Spiral learning divided into lecture, virtual and physical laboratory and connected via project to next session \cite{tarik2017} (b) robot assembly and (c) block-like programming style.}
  %\Description{.}
  \label{fig:tm}
\end{figure}

@@

\section{Conclusions and future work}
We introduced the term air4project as a project with the aim to tackle aspects for inclusion, accessibility, transparency, equity, fairness and participation of children in the fields of AI and Robotics as well as to create a more child-centre approach for AI and Robotics.
In this work, we also touched on the open source projects in AI and Robotics as a corner stone for AIR4Children with the aim of minimise cost of the materials and made customised educational material.  
Similarly, it has been presented the three phases for AIR4Children for piloting, implementing and refining workshops for children in the age range between 6 to 14. 
We also touched on the creation of curriculums with Montessori education, a non-traditional educational approach to help young audiences to develop skills such as think creatively with curiosity and open-minded as well as develop a have a sense of wonder and joy in learning.

For future plans, in the coming year, we will complete the first round of educational material for a child-centre AI and robotics where pilots, workshops and showcases are part of the 2021 and 2022 agenda.

>>>>

That said, figure \ref{fig:tm}(a) illustrates the spiral learning technique adopted for AIR4Children to reinforce the above Montessori skills \cite{tarik2017}.
\begin{figure}[h]
  \centering
  \includegraphics[width=\linewidth]{../figures/teaching-materials/versions/drawing-v00.png}
  \caption{(a) Spiral learning divided into lecture, virtual and physical laboratory and connected via project to next session \cite{tarik2017} (b) robot assembly and (c) block-like programming style.}
  %\Description{.}
  \label{fig:tm}
\end{figure}

% BLURS 
%Finding solutions together translate to social situations as well as it provides children with the foundations for decision making, logical reasoning, categorizing, analytical thinking, negotiation, and creativity. 
%In that way, AIR4Children's workshop integrates various hands-on activities where the children will develop different intellectual and social skills to incorporate into other areas of their lives.
%More specifically, such workshops are based on several Montessori principles such as: moving from the simple to the complex, the concrete to the abstract, the familiar to the unfamiliar and the general to the specific, as well as a mixed age group, where children can learn from each other.

@@

\section{Conclusions and future work}
We introduced the term air4project as a project with the aim to tackle aspects for inclusion, accessibility, transparency, equity, fairness and participation of children in the fields of AI and Robotics as well as to create teaching materials with a more child-centre approach for AI and Robotics.
We also touched on the open source projects in AI and Robotics as a corner stone for AIR4Children with the aim of minimise cost of the materials and made customised educational materials.  
Similarly, it has been presented the initial phases of AIR4Children that include piloting, implementing and refining workshops for children in the age range between 6 to 14 to be implemented in Xicohtzinco, a town from Tlaxcala, M\'exico.
We also touched on the creation of curriculums with Montessori education, a non-traditional educational approach to help young audiences to develop skills to think creatively with curiosity and open-minded as well as to develop a sense of wonder and joy in learning.

As a future work, air4children aims to run workshops by the end of 2021 to put in practice educational material of child-centre AI and robotics and to evaluate the impact on these fields to children and to the community.
